\begin{tcolorbox}[
        width=\textwidth,
        colback={gray!10},
        colframe=white,
        % title={\bf Profile:},
        % colbacktitle=yellow,
        % coltitle=blue,
        sharp corners,
        boxrule=0mm,
        arc=1mm,
    ]
    \begin{spacing}{1.2}
        % \small
        % \setlength{\columnsep}{5mm}
        \begin{multicols}{2}
            {\bf\large Profile:}
            % Getting insight from data.
            % Chemistry by training and physics at heart, speaking computer language.
            As a data scientist with a profound background in quantum chemistry, biophysics, and mathematics, I bring over eight years of experience to the table, having served as a scientific algorithm developer, data scientist, and team leader. My passion lies in extracting fundamental insights from data, thinking critically, and understanding the rationale behind each task. With my ability to learn quickly and motivation to take on challenges, I have excelled as an individual contributor, taking calculated risks and showing initiative. My experience spans consulting for a biotech startup and the financial industry, where I developed scientific software, validated scalable HPC algorithms, and worked collaboratively to deliver top-quality, data-driven scientific solutions and visualizations. I have a track record of solving complex problems through algorithm development in research labs in New Zealand, Argentina, and Colombia. In the role of a teacher, I've mentored students in two large universities, simplifying complex scientific concepts, methods, and theories in science, math, and computers. In my spare time, I enjoy intellectual pursuits like reading, writing, and learning new things. I am also freelance as an editor and reviewer for scientific manuscripts and research for publication.

            % \vspace*{-2mm}
            % \begin{flushright}
            %     \tiny
            %     Chemistry by training and physics at heart, speaking computer language
            % \end{flushright}
        \end{multicols}
    \end{spacing}
    \vspace*{-4mm}
\end{tcolorbox}