{\bf\Large Peer-reviewed \href{.}{Publications}}

\begin{itemize}
    % \itemsep-1mm
    \small

    \item \textbf{Flórez, Edison}; Zapata-Escobar, Andy; Ferraro, Franklin; Ibarguen-Becerra, César; Chamorro, Yuly; and Maldonado, Alejandro F.\emph{``Coordination of Mercury (II) in Water Promoted over Hydrolysis in Solvated Clusters [Hg(H$_2$O)$_{1-6}$]$^{2+}_{(aq)}$: Insights from Relativistic Effects and Free Energy Analysis.''} \href{.}{Submitted}

    \item \textbf{Flórez, Edison}; Reuvers, Tom; Schwarz, WH Eugen and Peter Schwerdtfeger. \emph{``The Stability of the Noble Gas Fluorides from Nonrelativistic and Relativistic Density Functional and Coupled Cluster Studies.''} \href{.}{Submitted}

    \item \textbf{Flórez, Edison}; Helgaker, Trygve; Klopper, Wim; Teale, Andrew; Stopkowicz, Stella; Pahl, Elke \emph{``Melting of Neon Under Extreme Conditions: Ab Initio Monte Carlo Simulations in High Magnetic Fields.''}. \href{.}{Submitted}
          %Florez, Edison, Trygve Helgaker, Wim Klopper, Andrew Teale, Stella Stopkowicz, and Elke Pahl. "Melting Under Extreme Conditions: Ab Initio Monte Carlo Simulations." In APS March Meeting Abstracts, vol. 2019, pp. C17-001. 2019.

    \item \textbf{Flórez, Edison}; Odile R. Smits; Jan-Michael Mewes; Paul Jerabek; and Peter Schwerdtfeger. \emph{``From the gas phase to the solid state: The chemical bonding in the superheavy element flerovium.''} The Journal of Chemical Physics 157, no. 6 (2022): 064304.\href{https://www.doi.org/10.1063/5.0097642}{DOI: 10.1063/5.0097642}

    \item Chamorro, Yuly;  \textbf{Flórez, Edison}; Alejandro F. Maldonado; Gustavo A. Aucar; and Albeiro Restrepo. \emph{``Microsolvation of heavy halides.''} International Journal of Quantum Chemistry 121, no. 7 (2021): e26571. \href{https://www.doi.org/10.1002/qua.26571}{DOI: 10.1002/qua.26571}

    \item \textbf{Flórez, Edison}; Alejandro F. Maldonado; Gustavo A. Aucar; Jorge David; and Albeiro Restrepo. \emph{``Microsolvation of methylmercury: structures, energies, bonding and NMR constants ($^{199}$Hg, $^{13}$C and $^{17}$O).''} Physical Chemistry Chemical Physics 18, no. 3 (2016): 1537-1550. \href{https://www.doi.org/10.1039/c5cp04826e}{DOI: 10.1039/c5cp04826e}

\end{itemize}


