\section{
    \colorbox{gray!20}{
        \parbox{0.98\linewidth}{
            Professional \href{.}{Experience}
        }
    }
}

\vspace*{-8mm}

\begin{itemize}[leftmargin=5mm]

        % ---------------------------------------------------------
        % METROVATE
        % ---------------------------------------------------------
    \item \textbf{\large Computational Lead}\hfill
        \href{.}{\bf May.2024 - Present}\\
        Metrovate [\href{https://www.metrovate.com/}{metrovate.com}],
        New Zealand

        \begin{itemize}[leftmargin=0mm]
                \small
                \setlength\itemsep{0.2em}

            \item \textbf{Platform Architecture:}
                Architecting a multi-cloud, microservices-based
                computational platform for \textit{de novo} peptide
                design. Orchestrating complex workflows (Target Prep,
                Docking, MD) using Nextflow,
                \textbf{Python}, and containerized environments
                (\textbf{Docker}).

            \item \textbf{Scientific Integration:}
                Integrating high-performance bioinformatics tools
                (e.g., \textbf{Boltz}, \textbf{RFDiffusion},
                    \textbf{DiffDock}, \textbf{GROMACS}, \textbf{QM/MM},
                etc.) into a cohesive API-driven ecosystem to
                generate and screen bioactive protein ``digital
                twins'' for agricultural use.

            \item \textbf{Strategic Leadership:} Bridging
                the gap between biological discovery and software
                engineering, defining the technical roadmap, and
                overseeing the deployment of scalable AI/ML pipelines.

        \end{itemize}

        \vspace{1mm}
        \textbf{\href{.}{\underline{Achievement:}}} Designed and
        deployed the company's flagship ``Digital Twin Pipeline'',
        reducing candidate design and discovery time from months to
        days by automating structural prediction and affinity scoring.

        % ---------------------------------------------------------
        % CORDIS
        % ---------------------------------------------------------
    \item \textbf{\large Sales Executive (Data Strategy Focus)}\hfill
        \href{.}{\bf Sep.2023 - Jun.2025}\\
        Cordis
        [\href{https://www.cordishotels.com/en/auckland/}{cordishotels.com}],
        New Zealand

        \begin{itemize}[leftmargin=0mm]
                \small
                \setlength\itemsep{0.2em}

            \item \textbf{Process Automation:} Engineered
                automated \textbf{ETL pipelines} using
                \textbf{Python} to scrape, clean, and consolidate
                fragmented sales data, reducing manual reporting time by 35\%.

            \item \textbf{Business Intelligence:}
                Developed interactive dashboards and queried CRM/PMS
                databases to identify high-value corporate segments,
                enabling data-driven targeting strategies.

            \item \textbf{Account Management:} Managed a
                portfolio of key corporate accounts, utilizing data
                insights to optimize revenue streams and improve
                client retention.

        \end{itemize}

        \vspace{1mm}
        \textbf{\href{.}{\underline{Achievement:}}} Surpassed monthly
        sales goals and contributed to an \textbf{8\% revenue
        increase} in the corporate segment by implementing a
        Python-backed lead scoring system.

        % ---------------------------------------------------------
        % HELICOBIO
        % ---------------------------------------------------------
    \item \textbf{\large Data Scientist}\hfill
        \href{.}{\bf Aug.2021 - Aug.2023}\\
        HelicoBio [\href{https://www.helico.bio}{helico.bio}],
        New Zealand

        \begin{itemize}[leftmargin=0mm]
                \small
                \setlength\itemsep{0.2em}

            \item \textbf{Full-Stack Science:}
                Orchestrated the full software development lifecycle
                (SDLC) for plant biology research tools, optimizing
                performance using \textbf{Python} and \textbf{C++}.

            \item \textbf{Pipeline Engineering:} Built and
                validated scalable data pipelines to analyze genomic
                data and protein function, directly supporting
                wet-lab experimental design.

            \item \textbf{Cross-Functional Collaboration:}
                Translated complex biological requirements into
                technical specifications, ensuring seamless
                deployment of new analysis functionalities.
        \end{itemize}

        \vspace{1mm}
        \textbf{\href{.}{\underline{Achievement:}}} Enhanced the
        protein screening workflow, reducing wet-lab validation
        cycles by \textbf{20\%} and accelerating the identification
        of viable candidates.

        % ---------------------------------------------------------
        % FREELANCE / EDITING
        % ---------------------------------------------------------
    \item \textbf{\large Scientific Editor (Freelance)}\\
        \href{.}{\bf Apr.2023 - Dec.2023}\hfill
        Enago [\href{https://www.enago.com/}{enago.com}]\\
        \href{.}{\bf Apr.2018 - Dec.2018}\hfill
        MDPI [\href{https://www.mdpi.com/}{mdpi.com}]

        \begin{itemize}[leftmargin=0mm]
                \small
                \setlength\itemsep{0.2em}
            \item Provide high-level substantive editing
                for scientific manuscripts, refining technical
                clarity, structure, and adherence to high-impact
                journal standards.
        \end{itemize}

        \vspace{1mm}
        \textbf{\href{.}{\underline{Achievement:}}} Consistently improved
        manuscript quality, contributing to a desk acceptance rate
        increase of \textbf{30\%} for client authors.

        % ---------------------------------------------------------
        % MASSEY
        % ---------------------------------------------------------
    \item \textbf{\large Lab Assistant and Demonstrator}\\
        \href{.}{\bf Aug.2018 - Mar.2020}\\
        Massey University [\href{www.massey.ac.nz}{massey.ac.nz}],\\
        New Zealand

        \begin{itemize}[leftmargin=0mm]
                \small
                \setlength\itemsep{0.2em}
            \item Developed Standard Operating Procedures
                (SOPs) for the Physics Lab and automated data
                analysis/reporting using \textbf{Jupyter Notebooks},
                \textbf{Pandas}, and \textbf{Matplotlib}.
        \end{itemize}

        % ---------------------------------------------------------
        % EY
        % ---------------------------------------------------------
    \item \textbf{\large Data Scientist}\hfill
        \href{.}{\bf Aug.2016 - Mar.2018}\\
        %   EY-ifb [\href{www.ey.com/en\_gl/ey-ifb}{ey.com}],
        EY (Ernst \& Young) [\href{www.ey.com}{ey.com}],
        Colombia.

        \begin{itemize}[leftmargin=0mm]
                \small
                \setlength\itemsep{0.2em}

            \item \textbf{Financial Modelling:} Designed
                and implemented complex mathematical models for
                banking clients (SAP environment) to optimize bond
                portfolios and address economic challenges.

            \item \textbf{Security \& Automation:}
                Developed a \textbf{Python} module to parse, clean,
                and encrypt sensitive financial datasets, generating
                automated test cases for user training.
        \end{itemize}

        \vspace{1mm}
        \textbf{\href{.}{\underline{Achievement:}}} The automated Python
        module \textbf{halved (50\% reduction)} the time required to
        design and deploy new training sessions for banking staff.

\end{itemize}
